Holomorphic field theories and higher algebra

### 2024-10-15 draft.tex
improved acknowledgments

>>>>

The prompt to write this survey came from Andrey Lazarev, and we thank him for his patience and encouragement during the long period of putting it together.

The National Science Foundation supported O.G. through DMS Grant 2042052 during the writing of this paper.
The Max Planck Institute for Mathematics has hosted both O.G. and B.W. throughout their careers, and it provided a wonderful environment for O.G. during the last stages of writing.
